Holomorphic field theories and higher algebra

### 2023-08-17 highervertexops.tex
typo

There is a more concrete way to describe this decomposition, 
modeled on the construction of spherical harmonics as representations of $SO(n)$.
Consider the differential operator
\beqn
\triangle = \del_{z_1} \del_{\lambda_1} + \del_{z_2} \del_{\lambda_2}
\eeqn
acting on $\C[z_i,\lambda_i]$;
it is inspired by the Laplacian on $\CC^2$ when we view $\lambda_i$ as a version of $\Bar{z_i}$.
This operator has weight zero and, in fact, it is $SL(2)$-equivariant.
\owen{I need to check this myself. If there's a slick way, we should include it.}
On the other hand, it maps $V_{a,b}$ to $V_{a-1,b-1}$, i.e., it changes the bigrading by~$(-1,-1)$.

@@

\subsection{Residues}

Define
\beqn
\op{Res} \colon \sfA \to \C[-1]
\eeqn
by the rules that $\op{Res}|_{\sfA^0} = 0$ and
\beqn
\op{Res} \left(f(z,\lambda) \omega \right) = p (f(z,\lambda)) (z=0) .
\eeqn

\begin{lem}
\label{lem:res} 
The following are true regarding the higher algebraic residue:
\begin{enumerate}
\item The residue is $\lie{sl}(2)$ invariant.
\item For $f \in \C[z_1,z_2]$ one has $\op{Res}(f \omega) = f(0)$.
\item For any $f \in \sfA$ one has $\op{Res}(\dbar f) = 0$.
\end{enumerate}
\end{lem}
\begin{proof}
Item (1) holds since $p$ is the $\lie{sl}(2)$-equivariant projection. 
For (2), note that for $f \in \C[z_1,z_2]$ that $p(f) = f$.

>>>>

There is a more concrete way to describe this decomposition, 
modeled on the construction of spherical harmonics as representations of $SO(n)$.
Consider the differential operator
\beqn
\triangle = \del_{z_1} \del_{\lambda_1} + \del_{z_2} \del_{\lambda_2}
\eeqn
acting on $\C[z_i,\lambda_i]$;
it is inspired by the Laplacian on $\CC^2$ when we view $\lambda_i$ as a version of $\Bar{z_i}$.
This operator has weight zero and, in fact, it is $SL(2)$-equivariant.
For example, notice that for any $g(z_i,\lambda_i)$ we have
\begin{align*}
(\del_{z_1} \del_{\lambda_1} + \del_{z_2} \del_{\lambda_2})(z_2 \del_{z_1} g - \lambda_1 \del_{\lambda_2}g )& = z_2 \del_{z_1}^2 \del_{\lambda_1} g - \del_{z_1} \del_{\lambda_2} g - \lambda_1 \del_{z_1} \del_{\lambda_1} \del_{\lambda_2} g \\ & \qquad + \del_{z_1} \del_{\lambda_2}  g + z_2 \del_{z_1} \del_{z_2} \del_{\lambda_2} g - \lambda_1 \del_{z_2} \del_{\lambda_2}^2 g 
\\ & = z_2 \del_{z_1}^2 \del_{\lambda_1} g - \lambda_1 \del_{z_1} \del_{\lambda_1} \del_{\lambda_2} g + z_2 \del_{z_1} \del_{z_2} \del_{\lambda_2} g - \lambda_1 \del_{z_2} \del_{\lambda_2}^2 g .
\end{align*}
Thus $[\triangle,\sff] = 0$.
Similarly, one can show that $[\triangle, \sfe] = 0$.
\owen{I need to check this myself. If there's a slick way, we should include it.} \brian{I gave a computational proof.}
On the other hand, it maps $V_{a,b}$ to $V_{a-1,b-1}$, i.e., it changes the bigrading by~$(-1,-1)$.

@@

\subsection{The higher algebraic residue}

Define
\beqn
\op{Res} \colon \sfA \to \C[-1]
\eeqn
by the rules that $\op{Res}|_{\sfA^0} = 0$ and
\beqn
\op{Res} \left(f(z,\lambda) \omega \right) = p (f(z,\lambda)) (z=0) .
\eeqn
This residue extends to the completion to give a map
\beqn
\op{Res} \colon \Hat\sfA \to \C[-1] .
\eeqn

\begin{lem}
\label{lem:res} 
The following are true regarding the higher algebraic residue:
\begin{enumerate}
\item The residue is $\lie{sl}(2)$ invariant.
\item For $f \in \C[[z_1,z_2]]$ one has $\op{Res}(f \omega) = f(0)$.
\item For any $f \in \sfA$ one has $\op{Res}(\dbar f) = 0$.
Thus $\op{Res}$ is a cochain map.
\end{enumerate}
\end{lem}
\begin{proof}
Item (1) holds since $p$ is the $\lie{sl}(2)$-equivariant projection. 
For (2), note that for $f \in \C[z_1,z_2]$ that $p(f) = f$.
